Qubit tests from classical codes

### 2023-01-04 quantum_codes_test.tex
updated Section 5, various other edits

\newcommand{\field}{\mathbb{F}}
\newcommand{\C}{\ensuremath{\mathbb{C}}}
\newcommand{\N}{\ensuremath{\mathbb{N}}}
\newcommand{\bbN}{\ensuremath{\mathbb{N}}}
\newcommand{\complex}{\ensuremath{\mathbb{C}}}
\newcommand{\real}{\ensuremath{\mathbb{R}}}
%\newcommand{\natural}{\ensuremath{\mathbb{N}}}

@@

\newcommand{\Inv}{\ensuremath{\textsc{Inv}}}
\newcommand{\GEN}{\ensuremath{\textsc{GEN}}}
\newcommand{\SAMP}{\ensuremath{\textsc{SAMP}}}
\newcommand{\epr}{\ensuremath{\textsc{epr}}}
\newcommand{\RM}{\ensuremath{\textsc{RM}}}

@@

@@

	We denote $\mM_\infty = \mM \overline{\otimes} B(\ell_2)$ \hnote{what do $\overline{\otimes}$ and $B(\ell_2)$ mean?} with (infinite) trace $\tau_\infty = \tau \otimes \Tr$ \hnote{what does infinite trace mean? also, should it be $\Tr$ or $\tr$?}. We identify $\mM$ with $\mM\otimes e_{1,1}\subset \mM_\infty$.

	We let $\field$ denote the field with two elements. For $u\in \F^n$ for some $n$, we write $|u|$ for the Hamming weight of $u$, i.e.\ the number of nonzero coordinates. For $a,b \in \field^k$, we write $a \cdot b$ to denote the inner product $\sum_{i=1}^k a_i b_i$.

@@

	A POVM on $\mM$ is a finite collection of positive semidefinite operators $\{P_i\}_{i\in \mI}$ such that $\sum_i P_i = 1_\mM$. A POVM is \emph{projective} if for all $i$, $P_i$ is a projection.

	Given a projective measurement $\{P_a\}_{a\in \field^k}$ and $b\in \field^k$ we let $\widehat{P}(b) = \sum_a (-1)^{a\cdot b} P_a$ be the associated observable. If $k=1$, we often use the shorthand $\widehat{P}$ for $\widehat{P}(1) = P_0-P_1$.

	\begin{definition}[Closeness]\label{def:close}
Let $\{A^i_a\}\subseteq \mM$ and $\{B^i_b\}\subseteq \mN$ be two families of projective measurements on  tracial algebras $(\mM,\tau^\mM)$ and $(\mN,\tau^\mN)$ respectively, indexed by the same set $i\in \mI$. For $\delta\geq0$ and $\mu$ a measure on $\mI$ we say that $\{A^i\}$ and $\{B^i\}$ are $(\delta,\mu)$-close if there exists a projection $P\in\mM_\infty$ of finite trace such that $\mN=P\mM_\infty P$ and $\tau^\mN=\tau_\infty/\tau_\infty(P)$, and a partial isometry $w\in P \mM_\infty 1_\mM$ such that 
\[ \Es{i\sim\mu} \sum_a \big\| A^i_a - w^* B^i_a w \big\|_2^2 \,\leq\,\delta\]
and 
\[\max\big\{ \tau^\mM(1_\mM-w^*w)\,,\; \tau^\mN(P-ww^*)\big\} \,\leq\, \delta\;.\]
If the measure $\mu$ is omitted then it is understood to be the uniform measure on $\mI$.
\end{definition}

@@

\begin{lemma}\label{lem:pull-back}
Let  $(\mM,\tau^\mM)$ be a tracial von Neumann algebra, $P\in\mM_\infty$ a projection of finite trace, $\mN=P\mM_\infty P$ and $\tau^\mN=\tau_\infty/\tau_\infty(P)$, and $w\in P \mM_\infty 1_\mM$ a partial isometry. Let 
\[ \eps = 1-\min\big\{ \tau^\mM\big(1_\mM - w^* w\big)\,,\;\tau^\mN\big( P- w w^*\big)\big\}\;.\]
 Then for any projective measurement $\{P_i\}$ on $\mN$, there is a projective measurement $\{Q_i\}$ on $\mM$ such that 
\[ \sum_i \big\| Q_i - w^* P_i w\big\|_2^2 \,=\, O(\eps)\;.\] 
\end{lemma}

\begin{proof}
If $\eps\geq \frac{1}{2}$ the conclusion is trivial (for a suitably large implicit constant), so assume $\eps<\frac{1}{2}$. 
Define 
\[\tilde{Q}_i = w^* P_i w  + \frac{1}{|\mI|}\big(1_\mM - w^* w\big) \in \mM\;.\]
Then $\{\tilde{Q}_i\}$ is a POVM on $\mM$. Moreover, 
\begin{align*}
\sum_{i} \tau\big( (\tilde{Q}_i)^2 \big) &\geq \sum_{i} \tau\big( \big(w^* P_i w \big)^2 \big) \\
&= \sum_{i} \tau\big(  w^* P_i w w^*P_i w \big)\\
&= \sum_i \tau\big(  w^* P_i  P P_i w \big) - \sum_i \tau\big( w^* P_i  ( P - w w^*) P_i w \big)\\
&\geq 1 - \eps -  \tau_\infty\Big(\big( P - w w^*\big)\Big(\sum_i  P_i w w^* P_i\Big)\Big)\\ 
&\geq 1- \eps- \tau_\infty\big( P- w w^*\big)\;,
\end{align*}
where the fourth line uses that $P_iPP_i=P_i$, $\sum_i P_i = \Id_\mN$ and the definition of $\eps$ for the first term, and cyclicity of the trace for the second, and the last uses $\|ww^*\|,\|\sum_i P_i\|_\infty\leq 1$. By assumption, 
\begin{align*}
\tau_\infty\big( P- w w^*\big) \,\leq\, \eps\, \tau_\infty(P)\,\leq \frac{\eps}{1-\eps}\;.
\end{align*}
where the last inequality is because by definition, $\tau^N(P)=1$, thus
\[1-\eps \,\leq\, \tau^\mN(ww^*) \,=\, \frac{\tau_\infty(ww^*)}{\tau_\infty(P)}\,=\, \frac{\tau_\infty(w^*w)}{\tau_\infty(P)}  \,\leq\, \frac{1}{\tau_\infty(P)}\]
\hnote{why is $ww^* \leq 1_\mM$? The input to $w^*$ is from $P$, which belongs to ${\mM}_{\infty}$}\tnote{I had forgotten to use cyclicity once; better?}
since $\tau^\mM$ is normalized and $w^*w\leq 1_\mM$. Overall, 
\[ \sum_{i} \tau\big( (\tilde{Q}_i)^2 \big) \,\geq\, 1-\eps-\frac{\eps}{1-\eps}\,\geq\, 1-3\eps\;.\]
To conclude we apply~\cite[Theorem 1.2]{de2021orthogonalization} to obtain a projective measurement $\{Q_i\}$ on $\mM$ such that 
\begin{equation*}
\sum_i \big\|{Q}_i - \tilde{Q}_i \big\|^2_2 \,=\, O(\eps)\;.
\end{equation*}
Finally,
\begin{align*}
\sum_i \big\|{Q}_i - w^*{P}_i w\big\|^2_2 &= \sum_i \Big\|{Q}_i - \tilde{Q}_i  + \frac{1}{|\mI|}\big(1_\mM - w^* w\big) \Big\|^2_2\\
&\leq  \sum_i 2\big\|{Q}_i - \tilde{Q}_i\big\|_2^2  + 2\frac{1}{|I|}\big\|1_\mM - w^* w\big\|_2^2 \\
&=  O(\eps)\;,
\end{align*}
where the second line is by the triangle inequality. 
\end{proof}

@@

\begin{definition}[Code]
A $[n,k,d]$ linear code \hnote{need to specify $\field$?}\tnote{I haven't fixed that completely yet, it depends on how the conversion to $\F_q$ works out. For now I used the macro $\field$ and I mean everything to be over $\F_2$. We can clarify once everything is fixed} is a $k$-dimensional subspace $\code\subseteq \field^n$ such that for every $u\in \code$ such that $u\neq 0$, $|u|\geq d$. Equivalently, we think of $\code$ as a linear map $\code:\field^k\to \field^n$. We write $G_\code \in \field^{k\times n}$ for the generator matrix defined by $ G_\code^T e_i =\code(e_i)$ for all $i\in\{1,\ldots,k\}$, where $\{e_1,\ldots,e_k\}$ is the standard basis of $\field^k$. 
\end{definition}

@@

\begin{definition}[Oracle machine]
A (non-adaptive) \emph{randomized oracle machine} $M$ is a Turing machine that has read access to two special tapes, the randomness tape and the proof tape. $M$ operates in two stages. In the first stage, $M$ accesses the randomness tape in state $\rand$ and returns a set $S=M(\rand)\subseteq\{1,\ldots,n\}$ of  indices of the proof tape. In the second stage $M$ reads the corresponding entries from the state $\pi$ of the proof tape and returns a value in $\{0,1\}$, which only depends on $S$ and $\pi_S$, not on $\rand$. We write $M(\rand,\pi)$ for the decisions taken by $M$ when the randomness tape is $\rand$ and the proof tape is $\pi$. We also write $M(S,\pi_S)\in\{0,1\}$ for the decision taken by $M$ when the chosen entries are $S$ and their values is $\pi_S$.   
\end{definition}

\begin{definition}[Codeword test]
Let $\code$ be an $[n,k,d]$ linear code, $\delta:[0,1]\to[0,1]$, and $r\in \N$.
A $r$-local $\delta$-tester for $\code$ is a \hnote{if we're using this Turing machine formalism, why restrict to non-adaptive?} non-adaptive randomized oracle machine $M$ that makes at most $r$ queries to its proof tape and satisfies the following conditions:
\begin{itemize} 
\item (Completeness:) For any $u\in \code$, $\Pr_\rand( M(\rand,u)=1)=1$.
\item (Soundness:) For any $\eps\geq 0$ and any $u\in \field^n$ that is within (Hamming) distance at least  $\eps$ from $\code$, $\Pr_\rand(M(\rand,u)=0)\geq \delta(\eps)$. 
\end{itemize}
\end{definition}

@@

\subsection{Quantum soundness}

\begin{definition}[Code representation]
Let $\code$ be an $[n,k,d]$ linear code. A \emph{representation} of $\code$ is a collection of projective measurements $\{A^i_a\}_{a\in\field} \subseteq\mM$ for $i\in\{1,\ldots,n\}$ such that the $\{A^i_a\}$ pairwise commute and $\sum_{c\in\code} \prod_{i=1}^n A^i_{c_i}=\Id$.\footnote{This implies that whenever $u\notin \code$, $\prod_i A^i_{u_i}=0$.} 
\end{definition}

\begin{definition}[$\eps$-local presentation]
Let $\code$ be an $[n,k,d]$ linear code and $M$ an $r$-local tester for $\code$. An \emph{$\eps$-local presentation of $(\code,M)$} is a collection of projective measurements $\{A^i_a\}_{a\in\field} \subseteq\mM$ for $i\in\{1,\ldots,n\}$ such that for any $S\subseteq\{1,\ldots,n\}$ of size $|S|\leq r$ there are $|S|$ pairwise commuting projective measurements $\{B^{S,i}_a\}_{i\in S}$ \hnote{the output alphabet is confusing here; here it seems like $a \in \field$ whereas below $a \in \F^S$.} and $\eps_S\geq 0$ such that 
\begin{itemize}
\item $\sum_{a\in \F^S} 1_{M(S,a)=1} \prod_{i\in S} B^{S,i}_{a_i}= \Id$
\item $\{A^i\}_{i\in S}$ and $\{B^{S,i}\}_{i\in S}$ are $\eps_S$-close
\end{itemize} 
and moreover $\Es{S\leftarrow M(\cdot)} \eps_S \leq \eps$. \hnote{The $1_{M(S,a)=1}$ notation conflicts with the $1_{\mM}$ notation above. Also sometimes $I$ is used, othertimes $1$ is used.}
\end{definition}

@@

\subsection{Example: the Hadamard code}

We give an example of a family of quantum sound codes, the \emph{Hadamard codes}. This code can be defined for any  $k\geq 1$ and it is an $[K,k,K/2]_2$ linear code, where $K=2^k$. For simplicity we write  $\code_\had$ for it, omitting $k$. As a linear map, for $i\in\{1,\ldots,k\}$, $\code_\had(e_i) = (x_i)_{x\in \field^k} \in \field^K$, where we identify the index set $\{1,\ldots,K\}$ with the set $\field^k$ in an arbitrary way.

It is shown in~\cite{blum1990self} that the following randomized oracle machine $M_\had$ is a $3$-local $\delta$-tester for $\code_\had$, where $\delta(\eps)=6\eps$. $M$ first uses its random tape to select $x,y\in\field^k$uniformly at random and returns the set $S=\{x,y,x+y\}$. For $\pi\in \field^K$, $M(S,\pi_S)$ accepts if and only if $\pi_x + \pi_y  = \pi_{x+y}$.

Using~\cite[Theorem 10]{natarajan2016robust} it follows that $M$ has quantum soundness $O(\eps)$.\footnote{While~\cite{natarajan2016robust} only show the result for finite-dimensional $\mM$, the same proof works for any $(\mM,\tau)$.}

@@

\begin{definition}
Let $k\in \N$ and $\delta:[0,1]\to\R_+$. 
A $(k,\delta(\eps))$-qubit test is a synchronous game $G=(\mX,\mu,\mA,D)$ such there are two sets $S_X,S_Z\subseteq \field^k$ and an injection $\phi:(\{X\}\times S_Z) \cup (\{Z\}\times S_Z) \to \mX$ such that $\mA(\phi({X},a))=\mA(\phi({Z},b))=\field$ for all $a\in S_X$, $b\in S_Z$ and such that the following holds:
\begin{itemize}
\item (Completeness:) There is a synchronous strategy for $G$ on $\mM=M_{2^{k}}(\C)$ that succeeds with probability $1$ in $G$ and is such that $\widehat{P^{\phi({W},a)}} = \tau^W(a)$ \hnote{overloading $\tau$}\tnote{Since the Paulis are binary we can just use $\sigma$ everywhere} for every $W\in\{X,Z\}$ and $a\in S_W$.
\item (Soundness:) Any synchronous strategy in $(\mM,\tau)$ for $G$ that succeeds with probability $1-\eps$ for some $\eps\geq 0$ is $\delta(\eps)$-close to a strategy on an algebra of the form $(M_{2^{k}}(\C)\otimes \mN,\tr\otimes \tau')$ and such that
\[\widehat{P^{\phi({W},a)}} = \tau^W(a)\otimes \Id_\mN\;.\]
\end{itemize}
\end{definition}

@@

\begin{theorem}
Let $\code$ be an $[n,k,d]$ linear code and $M$ an $r$-local tester for $\code$ that is $\delta(\eps)$-quantum sound and such that $\code,M)$ is Abelian. Then the braiding test over $\code$ is a $(k,\delta')$-qubit test, where $S_X=S_Z=\{G_\code e_i:\,i\in\{1,\ldots,n\}\}\subseteq \field^k$, $\phi(W,G_\code e_i)=(W,i)$ and $\delta' = O(\delta^{1/2}(6\eps))$.\footnote{Assume $G_\code$ has no repeated columns.} 
\end{theorem}

@@

To conclude we show that this strategy succeeds in the game $G_{\dlS}$ with probability $1-O(\sqrt{\delta_1})$. Assuming that this has been shown, by~\cite[Corollary 3.9]{de2022spectral} the strategy $\strategy'$ is $O(\sqrt{\delta_1})$-close to a strategy $\strategy''$ on an algebra of the form $(M_{2^{k}}(\C)\otimes \mN,\tr\otimes \tau')$ such that $P^W_b = \tau^W_b\otimes 1_\mN$. By definition of $R$, 
\begin{equation}\label{eq:main-3}
 Q^{W,i}_b \,=\,  \sum_{a:\,a_i=b}  Q^W_a \,=\, \sum_{c: (G_\mC^T c)_i=b}  R^W_c \;,
\end{equation}
hence
\begin{equation*}
 \widehat{Q^{W,i}}\,=\, \sum_c (-1)^{c\cdot (G_\mC e_i)} R^W_c \,=\, \widehat{R^W}(G_\mC e_i)\;.
\end{equation*}
Using the definition of the game distribution, closeness of $\strategy'$ and $\strategy''$ thus implies that
\begin{equation*}
\Es{i\in\{1,\ldots,n\}} \big\|\widehat{Q^{W,i}} - (w'')^* {\tau^W}(G_\mC e_i) (w'') \big\|_2^2 \,=\,O(\sqrt{\delta_1})\;.
\end{equation*}
Combining with~\eqref{eq:main-0} and~\eqref{eq:main-1}, this shows the theorem.

@@

\subsection{Finite fields}

For $q=2^t$ and $a\in \field$ we let $\kappa(a)$ denote the binary representation of $a$, where the representation is taken in a self-dual normal basis of $\field$ over $\F_2$. We extend $\kappa$ to vectors over $\field$ coordinate-wise.

	We use $\tau^W(a)$, $a\in F_q^k$, to denote the tensor product of $k$ Pauli $W$ observables over $\field$. We use $\tau^W_a$ to denote the associated projective measurement.

>>>>

\newcommand{\field}{\mathbb{F}_2}
\newcommand{\C}{\ensuremath{\mathbb{C}}}
\newcommand{\N}{\ensuremath{\mathbb{N}}}
\newcommand{\bbN}{\ensuremath{\mathbb{N}}}
\newcommand{\complex}{\ensuremath{\mathbb{C}}}
\newcommand{\real}{\ensuremath{\mathbb{R}}}
%\newcommand{\natural}{\ensuremath{\mathbb{N}}}

@@

\newcommand{\Inv}{\ensuremath{\textsc{Inv}}}
\newcommand{\GEN}{\ensuremath{\textsc{GEN}}}
\newcommand{\SAMP}{\ensuremath{\textsc{SAMP}}}
\newcommand{\epr}{\ensuremath{\textsc{epr}}}
\newcommand{\RM}{\ensuremath{\textsc{RM}}}
\newcommand{\Had}{\ensuremath{\textsc{Had}}}
\newcommand{\HRM}{\ensuremath{\textsc{HRM}}}

@@

\subsection{Notation}

When we write $\Es{i\in \mX}$ where $\mX$ is a finite set, we mean the expectation over $i$ chosen uniformly at random from $\mX$, i.e.\ $\frac{1}{|\mX|} \sum_{i\in \mX}$.

@@

	Let $B(\ell_2)$ be the von Neumann algebra of bounded operators on $\ell_2$, the Hilbert space of convergent sequences in $\C^\Z$ equipped with the usual Euclidean norm. We denote $\mM_\infty = \mM \overline{\otimes} B(\ell_2)$, where the overline denotes closure for the operator topology. $\mM_\infty$ is a von Neumann algebra equipped with the (infinite) trace $\tau_\infty = \tau \otimes \Tr$, with $\Tr(x)=\sum_{i\in \Z} e_i^T X e_i$ the trace on $B(\ell_2)$. We generally identify $\mM$ with the ``corner'' $\mM\otimes e_{1,1}\subset \mM_\infty$.

	We let $\F$ denote a finite field, and $\field$ the field with two elements. For $u\in \F^n$ for some $n$, we write $|u|$ for the Hamming weight of $u$, i.e.\ the number of nonzero coordinates. For $a,b \in \F^k$, we write $a \cdot b$ to denote the inner product $\sum_{i=1}^k a_i b_i$.

@@

	A POVM on $\mM$ is a finite collection of positive semidefinite operators $\{P_i\}_{i\in \mI}$ such that $\sum_i P_i = \Id_\mM$. A POVM is \emph{projective} if for all $i$, $P_i$ is a projection. 
	Given a projective measurement $\{P_a\}_{a\in \field^k}$ and $b\in \field^k$ we let $\widehat{P}(b) = \sum_a (-1)^{a\cdot b} P_a$ be the associated observable. If $k=1$, we often use the shorthand $\widehat{P}$ for $\widehat{P}(1) = P_0-P_1$.

	A specific family of measurements on $M_{2^k}(\C)$ is derived from the \emph{Pauli observables}. Define 
	\[ \sigma^X = \begin{pmatrix} 0 & 1 \\ 1 & 0 \end{pmatrix}\;,\qquad \sigma^Z = \begin{pmatrix} 1 & 0 \\ 0 & -1\end{pmatrix}\;,\]
	and more generally for $a,b\in \F_2^k$ let $\sigma^X(a) = \otimes_{i=1}^t (\sigma^X)^{a_i}$ and $\sigma^Z(b) = \otimes_{i=1}^t (\sigma^Z)^{b_i}$. We slightly abuse notation and write 
	\[ \sigma^X_a = \Es{\alpha\in\F_2^t} (-1)^{a\cdot \alpha} \sigma^X(\alpha)\qquad\text{and}\qquad\sigma^Z_b = \Es{\beta\in\F_2^t} (-1)^{b\cdot\beta} \sigma^Z(\beta)\]
	for the associated POVM elements.

	\begin{definition}[Closeness]\label{def:close}
Let $\{A^i_a\}\subseteq \mM$ and $\{B^i_a\}\subseteq \mN$ be two families of projective measurements on  tracial algebras $(\mM,\tau^\mM)$ and $(\mN,\tau^\mN)$ respectively, indexed by the same set $i\in \mI$ and with the same set of outcomes $a,b\in\mA$. For $\delta\geq0$ and $\mu$ a measure on $\mI$ we say that $\{A^i\}$ and $\{B^i\}$ are $(\delta,\mu)$-close if there exists a projection $P\in\mM_\infty$ of finite trace such that $\mN=P\mM_\infty P$ and $\tau^\mN=\tau_\infty/\tau_\infty(P)$, and a partial isometry $w\in P \mM_\infty \Id_\mM$ such that 
\[ \Es{i\sim\mu} \sum_{a\in\mA} \big\| A^i_a - w^* B^i_a w \big\|_2^2 \,\leq\,\delta\]
and 
\[\max\big\{ \tau^\mM(\Id_\mM-w^*w)\,,\; \tau^\mN(P-ww^*)\big\} \,\leq\, \delta\;.\]
If the measure $\mu$ is omitted then it is understood to be the uniform measure on $\mI$.
\end{definition}

@@

\begin{lemma}\label{lem:pull-back}
Let  $(\mM,\tau^\mM)$ be a tracial von Neumann algebra, $P\in\mM_\infty$ a projection of finite trace, $\mN=P\mM_\infty P$ and $\tau^\mN=\tau_\infty/\tau_\infty(P)$, and $w\in P \mM_\infty \Id_\mM$ a partial isometry. Let 
\[ \eps = 1-\min\big\{ \tau^\mM\big(\Id_\mM - w^* w\big)\,,\;\tau^\mN\big( P- w w^*\big)\big\}\;.\]
 Then for any projective measurement $\{P_i\}$ on $\mN$, there is a projective measurement $\{Q_i\}$ on $\mM$ such that 
\[ \sum_i \big\| Q_i - w^* P_i w\big\|_2^2 \,=\, O(\eps)\;.\] 
\end{lemma}

\begin{proof}
If $\eps\geq \frac{1}{2}$ the conclusion is trivial (for a suitably large implicit constant), so assume $\eps<\frac{1}{2}$. 
Define 
\[\tilde{Q}_i = w^* P_i w  + \frac{1}{|\mI|}\big(\Id_\mM - w^* w\big) \in \mM\;.\]
Then $\{\tilde{Q}_i\}$ is a POVM on $\mM$. Moreover, 
\begin{align*}
\sum_{i} \tau\big( (\tilde{Q}_i)^2 \big) &\geq \sum_{i} \tau\big( \big(w^* P_i w \big)^2 \big) \\
&= \sum_{i} \tau\big(  w^* P_i w w^*P_i w \big)\\
&= \sum_i \tau\big(  w^* P_i  P P_i w \big) - \sum_i \tau\big( w^* P_i  ( P - w w^*) P_i w \big)\\
&\geq 1 - \eps -  \tau_\infty\Big(\big( P - w w^*\big)\Big(\sum_i  P_i w w^* P_i\Big)\Big)\\ 
&\geq 1- \eps- \tau_\infty\big( P- w w^*\big)\;,
\end{align*}
where the fourth line uses that $P_iPP_i=P_i$, $\sum_i P_i = \Id_\mN$ and the definition of $\eps$ for the first term, and cyclicity of the trace for the second, and the last uses $\|ww^*\|,\|\sum_i P_i\|_\infty\leq 1$. By assumption, 
\begin{align*}
\tau_\infty\big( P- w w^*\big) \,\leq\, \eps\, \tau_\infty(P)\,\leq \frac{\eps}{1-\eps}\;.
\end{align*}
where the last inequality is because by definition, $\tau^N(P)=1$, thus
\[1-\eps \,\leq\, \tau^\mN(ww^*) \,=\, \frac{\tau_\infty(ww^*)}{\tau_\infty(P)}\,=\, \frac{\tau_\infty(w^*w)}{\tau_\infty(P)}  \,\leq\, \frac{1}{\tau_\infty(P)}\]
\hnote{why is $ww^* \leq 1_\mM$? The input to $w^*$ is from $P$, which belongs to ${\mM}_{\infty}$}\tnote{I had forgotten to use cyclicity once; better?}
since $\tau^\mM$ is normalized and $w^*w\leq 1_\mM$. Overall, 
\[ \sum_{i} \tau\big( (\tilde{Q}_i)^2 \big) \,\geq\, 1-\eps-\frac{\eps}{1-\eps}\,\geq\, 1-3\eps\;.\]
To conclude we apply~\cite[Theorem 1.2]{de2021orthogonalization} to obtain a projective measurement $\{Q_i\}$ on $\mM$ such that 
\begin{equation*}
\sum_i \big\|{Q}_i - \tilde{Q}_i \big\|^2_2 \,=\, O(\eps)\;.
\end{equation*}
Finally,
\begin{align*}
\sum_i \big\|{Q}_i - w^*{P}_i w\big\|^2_2 &= \sum_i \Big\|{Q}_i - \tilde{Q}_i  + \frac{1}{|\mI|}\big(1_\mM - w^* w\big) \Big\|^2_2\\
&\leq  \sum_i 2\big\|{Q}_i - \tilde{Q}_i\big\|_2^2  + 2\frac{1}{|I|}\big\|1_\mM - w^* w\big\|_2^2 \\
&=  O(\eps)\;,
\end{align*}
where the second line is by the triangle inequality. 
\end{proof}

@@

\begin{definition}[Code]
For $q$ a prime power and $n,k,d$ integer
a $[n,k,d]_q$ linear code is a $k$-dimensional subspace $\code\subseteq \F_q^n$ such that for every $u\in \code$ such that $u\neq 0$, $|u|\geq d$. Equivalently, we think of $\code$ as a linear map $\code:\F_q^k\to \F_q^n$. We write $G_\code \in \F_q^{k\times n}$ for the generator matrix defined by $ G_\code^T e_i =\code(e_i)$ for all $i\in\{1,\ldots,k\}$, where $\{e_1,\ldots,e_k\}$ is the standard basis of $\F_q^k$. 
\end{definition}

When the subscript $q$ is omitted, it is implicitly taken as $q=2$, i.e.\ the code is assumed to be binary.

@@

%\begin{definition}[Oracle machine]
%A (non-adaptive) \emph{randomized oracle machine} $M$ is a Turing machine that has read access to two special tapes, the randomness tape and the proof tape. $M$ operates in two stages. In the first stage, $M$ accesses the randomness tape in state $\rand$ and returns a set $S=M(\rand)\subseteq\{1,\ldots,n\}$ of  indices of the proof tape. In the second stage $M$ reads the corresponding entries from the state $\pi$ of the proof tape and returns a value in $\{0,1\}$, which only depends on $S$ and $\pi_S$, not on $\rand$. We write $M(\rand,\pi)$ for the decisions taken by $M$ when the randomness tape is $\rand$ and the proof tape is $\pi$. We also write $M(S,\pi_S)\in\{0,1\}$ for the decision taken by $M$ when the chosen entries are $S$ and their values is $\pi_S$.   
%\end{definition}

\begin{definition}[Codeword test]\label{def:code-test}
Let $\code$ be an $[n,k,d]_q$ linear code, $\delta:[0,1]\to[0,1]$, and $r\in \N$.
An $r$-local $\delta$-tester for $\code$ is a distribution $\nu$ over subsets $S\subseteq [n]$ of size at most $r$, and for each $S$ in the support of $\nu$ a predicate $M(S,\cdot):\F_q^S\to\{0,1\}$, such that the following hold:
\begin{itemize} 
\item (Completeness:) For any $u\in \code$, $\Pr_{S\sim \nu}( M(S,u_S)=1)=1$.
\item (Soundness:) For any $\eps\geq 0$ and any $u\in \F_q^n$ that is within (Hamming) distance at least  $\eps$ from $\code$, $\Pr_{S\sim\nu}(M(S,u_{|S})=0)\geq \delta(\eps)$. 
\end{itemize}
\end{definition}

@@

\subsection{Quantum soundness}
\label{sec:q-soundness}

\begin{definition}[Code representation]
Let $\code$ be an $[n,k,d]$ linear code. A \emph{representation} of $\code$ is a collection of projective measurements $\{A^i_a\}_{a\in\F_q} \subseteq\mM$ for $i\in\{1,\ldots,n\}$ such that the $\{A^i_a\}$ pairwise commute and $\sum_{c\in\code} \prod_{i=1}^n A^i_{c_i}=\Id$.\footnote{This implies that whenever $u\notin \code$, $\prod_i A^i_{u_i}=0$.} 
\end{definition}

\begin{definition}[$\eps$-local presentation]
Let $\code$ be an $[n,k,d]_q$ linear code and $M$ an $r$-local tester for $\code$ with distribution $\nu$. An \emph{$\eps$-local presentation of $(\code,M)$} is a collection of projective measurements $\{A^i_a\}_{a\in\F_q} \subseteq\mM$ for $i\in\{1,\ldots,n\}$ such that for any $S\subseteq\{1,\ldots,n\}$ of size $|S|\leq r$ there are $|S|$ pairwise commuting projective measurements $\{B^{S,i}_b\}_{b\in \F_q}$, for $i\in S$, such that 
\begin{itemize}
\item $\sum_{a\in \F^S} 1_{M(S,a)=1} \prod_{i\in S} B^{S,i}_{a_i}= \Id$
\item The two families $\{A^i\}_{S, i\in S}$ and $\{B^{S,i}\}_{S, i\in S}$ are $(\eps,\nu')$-close, where $\nu'((S,i))=\nu(S)1_{i\in S}\frac{1}{|S|}$.
\end{itemize} 
\hnote{The $1_{M(S,a)=1}$ notation conflicts with the $1_{\mM}$ notation above. Also sometimes $I$ is used, othertimes $1$ is used.}\tnote{fixed, now always using $\Id$ for the identity}
\end{definition}

@@

\subsection{Example: the Hadamard code}
\label{sec:had}

We give an example of a family of quantum sound codes, the \emph{Hadamard codes}. This code can be defined for any  $t\geq 1$ and it is an $[T,t,T/2]_2$ linear code, where $T=2^t$. For simplicity we write  $\code_\had$ for it, omitting $t$. As a linear map, for $i\in\{1,\ldots,t\}$, $\code_\had(e_i) = (x_i)_{x\in \field^t} \in \field^T$, where we identify the index set $\{1,\ldots,T\}$ with the set $\field^t$ in an arbitrary way.

It is shown in~\cite{blum1990self} that the following randomized oracle machine $M_\had$ is a $3$-local $\delta$-tester for $\code_\had$, where $\delta(\eps)=6\eps$. $M$ first uses its random tape to select $x,y\in\field^k$uniformly at random and returns the set $S=\{x,y,x+y\}$. For $\pi\in \field^T$, $M(S,\pi_S)$ accepts if and only if $\pi_x + \pi_y  = \pi_{x+y}$.

The following appears as~\cite[Theorem 10]{natarajan2016robust}.\footnote{While~\cite{natarajan2016robust} only show the result for finite-dimensional $\mM$, the same proof works for any $(\mM,\tau)$.}

\begin{theorem}
$M_\had$ has quantum soundness $O(\eps)$.
\end{theorem}

@@

\begin{definition}
Let $k\in \N$ and $\delta:[0,1]\to\R_+$. 
A $(k,\delta(\eps))$-qubit test is a synchronous game $G=(\mX,\mu,\mA,D)$ such there are two sets $S_X,S_Z\subseteq \field^k$ and an injection $\phi:(\{X\}\times S_Z) \cup (\{Z\}\times S_Z) \to \mX$ such that $\mA(\phi({X},a))=\mA(\phi({Z},b))=\field$ for all $a\in S_X$, $b\in S_Z$ and such that the following holds:
\begin{itemize}
\item (Completeness:) There is a synchronous strategy for $G$ on $\mM=M_{2^{k}}(\C)$ that succeeds with probability $1$ in $G$ and is such that $\widehat{P^{\phi({W},a)}} = \sigma^W(a)$ \hnote{overloading $\tau$}\tnote{Fixed; since the Paulis are binary we can just use $\sigma$ everywhere} for every $W\in\{X,Z\}$ and $a\in S_W$.
\item (Soundness:) Any synchronous strategy in $(\mM,\tau)$ for $G$ that succeeds with probability $1-\eps$ for some $\eps\geq 0$ is $\delta(\eps)$-close to a strategy on an algebra of the form $(M_{2^{k}}(\C)\otimes \mN,\tr\otimes \tau')$ and such that
\[\widehat{P^{\phi({W},a)}} = \sigma^W(a)\otimes \Id_\mN\;.\]
\end{itemize}
\end{definition}

@@

\begin{theorem}\label{thm:main}
Let $\code$ be an $[n,k,d]$ linear code and $M$ an $r$-local tester for $\code$ that is $\delta(\eps)$-quantum sound and such that $(\code,M)$ is Abelian. Then the braiding test over $\code$ is a $(k,\delta')$-qubit test, where $S_X=S_Z=\{G_\code e_i:\,i\in\{1,\ldots,n\}\}\subseteq \field^k$, $\phi(W,G_\code e_i)=(W,i)$ and $\delta' = O(\delta^{1/2}(6\eps))$.\footnote{Assume $G_\code$ has no repeated columns.} 
\end{theorem}

@@

To conclude we show that this strategy succeeds in the game $G_{\dlS}$ with probability $1-O(\sqrt{\delta_1})$. Assuming that this has been shown, by~\cite[Corollary 3.9]{de2022spectral} the strategy $\strategy'$ is $O(\sqrt{\delta_1})$-close to a strategy $\strategy''$ on an algebra of the form $(M_{2^{k}}(\C)\otimes \mN,\tr\otimes \tau')$ such that $P^W_b = \tau^W_b\otimes 1_\mN$. By definition of $R$, 
\begin{equation}\label{eq:main-3}
 Q^{W,i}_b \,=\,  \sum_{a:\,a_i=b}  Q^W_a \,=\, \sum_{c: (G_\mC^T c)_i=b}  R^W_c \;,
\end{equation}
hence
\begin{equation*}
 \widehat{Q^{W,i}}\,=\, \sum_c (-1)^{c\cdot (G_\mC e_i)} R^W_c \,=\, \widehat{R^W}(G_\mC e_i)\;.
\end{equation*}
Using the definition of the game distribution, closeness of $\strategy'$ and $\strategy''$ thus implies that
\begin{equation*}
\Es{i\in\{1,\ldots,n\}} \big\|\widehat{Q^{W,i}} - (w'')^* {\sigma^W}(G_\mC e_i) (w'') \big\|_2^2 \,=\,O(\sqrt{\delta_1})\;.
\end{equation*}
Combining with~\eqref{eq:main-0} and~\eqref{eq:main-1}, this shows the theorem.

@@

For $q=2^t$ and $a\in \field$ we let $\kappa(a)\in\F_2^t$ denote the binary representation of $a$, taken in a fixed but usually implicit self-dual basis of $\F_2^t$ over $\F_2$. We extend $\kappa$ to vectors over $\field$ coordinate-wise. We let $\tr(\cdot):\F_q\to\F_2$ denote the trace over $\F_2$. Because we chose a self-dual basis for the binary representation, the trace satisfies $\tr(ab)=\kappa(a)\cdot\kappa(b)$.

%	We use $\sigma^W(a)$, for $a\in F_q^k$, to denote the tensor product of $k$ Pauli $W$ observables over $\field$. We use $\{\sigma^W_a\}$ to denote the associated projective measurement.
